\chapter{Legal Issues}
Contrary to widespread myth, it is not a felony to possess lockpicks. Each state has its own
laws with respect to such burglarious instruments. Here is the Massachusetts version quoted
in entirety from the Massachusetts general code:

\begin{quote}
    \begin{center}
        Chapter 266 (crimes against property)

        Section 49. Burglarious instruments; making; possession; use.
    \end{center}


    Whoever makes or mends, or begins to make or mend, or knowingly has in
    his possession, an engine, machine, tool or implement adapted and designed for
    cutting through, forcing or breaking open a building, room, vault, safe or other
    depository, IN ORDER TO STEAL THEREFROM money or other property, or
    to commit any other crime, knowing the same to be adapted and designed for
    the purpose aforesaid, WITH INTENT TO USE OR EMPLOY OR ALLOW
    the same to be used or employed for such purpose, or whoever knowingly has in
    his possession a master key designed to fit more than one motor vehicle, WITH
    INTENT, TO USE OR EMPLOY THE SAME to steal a motor vehicle or other
    property therefrom, shall be punished by imprisonment in the state prison for
    not more than ten years or by a fine of not more than one thousand dollars and
    imprisonment in jail for not more than two and one half years.
\end{quote}

Emphasis added.

In other words, mere possession means nothing. If they stop you for speeding or something,
and find a pick set, they can't do much. On the other hand, if they catch you picking
the lock on a Monec machine they get to draw and quarter you.

States with similar wording include ME, NH, NY. One place that DOES NOT have
similar wording, and does make possession illegal, is Washington, DC. These are the only
other places I have checked. I would imagine that most states are similar to Massachusetts,
but I would not bet anything substantial (say, more than a slice of pizza) on it.

It may be a good idea to carry around a xeroxed copy of the appropriate page from your
state's criminal code.
